\TheTitle

### 2016-04-22 linvis.tex
Editing Future Work

There are still many areas that can be improved before the full potential of our
model can be realized. Here, we outline various areas that still need more
attention.

@@

There is currently no functionality surrounding searching by filename. Use-case 2
may know what file they are editing and try to determine how it may work with the
other commits and merges in the module. It is possible that a third use-case may
arise, where the user wants to determine all commits that effect a given file. In
both cases, a bottom-to-top approach is used. With this functionality, implementing
the top-to-bottom search feature becomes trivial.

There is limited functionality to the presentation of the file information. At a
minimum, the patches for the commits can be displayed. From there, the patches can
be used to piece together parts of the file to generate a single patch at a given
merge rather than displaying each patch individually. The patches can also be used
for determining what kinds of changes were made, if the lines are being added,
removed, or replaced.

@@

Our model can aggregate more information than what we have implemented. The
authorship information is important for licensing purposes, and we can show all
authors contributing to a merge and how many commits they contributed to the merge.
We could go further, providing information about what files they edited, how many
lines they added and removed, and more.

\subsection{Diff generation}

Due to the construction of the tree, it is possible to generate a diff of a given
file in a merge. This would remove areas that overlap, and provide users with a
single patch at a merge rather than attempting to combine all of the diff files from
the leaves.

>>>>

There are still many areas that can be improved before the full potential of our
model can be realized. Here, we outline various areas of the tool that still need
more attention.

@@

There is currently no functionality surrounding searching by filename. Users falling
under use-case 2 may know what file they are editing and try to determine how it may
work with the other commits and merges in the module. It is possible that a third
use-case may arise, where the user wants to determine all commits that effect a
given file. In both cases, bottom-to-top approach is applied.

There is limited functionality to the presentation of the file information. At a
minimum, the patches for the commits can be displayed. From there, the patches can
be used to piece together parts of the file to generate a single patch at a given
merge rather than displaying each patch individually. The patches can also be used
for determining what kinds of changes were made, if the lines are being added,
removed, or being replaced.

@@

Our model can aggregate more information than what we have implemented. The
authorship information is important for licensing purposes, and we can show all
authors contributing to commits in a  merge and how many commits they contributed to
the merge. We could go further, providing information about what files they edited,
how many lines they added and removed, and more.
